\section*{References}

\begin{thebibliography}{1}
\bibitem{ipv6wg} {\tt http://hepix-ipv6.web.cern.ch}
\bibitem{ipv6chep2013} S Campana et al 2014 J. Phys.: Conf. Ser. {\bf513} 062026
\bibitem{ripeness} The status of IPv6 readiness of the local Internet Registries
that refer to RIPE is monitored in the ``IPv6 RIPEness'' pages ({\tt https://ipv6ripeness.ripe.net/} at the time of writing). 
\bibitem{ripestat} RIPE provides access to a comprehensive set of statistical
data via {\tt https://stat.ripe.net/data}. This data set is also used for
the online diagnostics and statistical tools (e.g. BGPlay). 
\bibitem{ripeipv6} Specific
IPv6 trend graphs for the RIPE LIRs can be accessed at\\ {\tt https://labs.ripe.net/statistics/?tags=ipv6}.
\bibitem{arinstat} A collection of trend plots collected by ARIN
can be found here:\\ {\tt https://www.arin.net/knowledge/statistics/}.
\bibitem{apnicstat} A somewhat out-of-date set of IPv6
statistics data gathered by APNIC can be found here:\\ {\tt https://labs.apnic.net/ipv6-measurement/}.
\bibitem{lacnicipc6} The LACNIC IPv6 portal is at:\\ {\tt http://portalipv6.lacnic.net/en/}.
\bibitem{afrinicipv6} A collection of AFRINIC IPv6 resources can be found here:\\  {\tt http://www.afrinic.net/en/services/statistics/ipv6-resources}.
\bibitem{akamaistats} The historical statistics of IPv6 traffic on Akamai usare are recorded at {\tt http://www.akamai.com/ipv6/} at the time of writing.
\bibitem{googlestats} The historical statistics of IPv6 client traffic on Google are recorded at\\ {\tt http://www.google.com/intl/en/ipv6/statistics.html} at the time of writing.
\bibitem{LHCassumption} WLCG pre-GDB - IPv6 Workshop (A. Dewhurst et al.), {\tt https://indico.cern.ch/event/313194/session/1/contribution/3/0/material/slides/0.pdf}
\bibitem {middleware}  { \tt https://wiki.egi.eu/wiki/Middleware\_products\_verified\_for\_the\_support\_of\_IPv6 , http://hepix-ipv6.web.cern.ch/wlcg-applications}
\bibitem {LHCb} LHCb Collab. (A. Alves et al.), JINST 3, S08005 (2008), {\tt http://dx.doi.org/10.1088/1748-0221/3/08/S08005}
\bibitem {[DIRAC} DIRAC: a community grid solution (A. Tsaregorodtsev et al.), 2008 J. Phys.: Conf. Ser. 119 062048, {\tt http://iopscience.iop.org/1742-6596/119/6/062048}
\bibitem{readiness} Our working group tracks the IPv6 readiness of applications
of interest to WLCG at\\ {\tt http://hepix-ipv6.web.cern.ch/wlcg-applications}.
\bibitem{rfc} All Internet Engineering Task Force Requests For Comments (RFC) documents are available
from URLs such as http://www.ietf.org/rfc/rfcNNNN.txt where NNNN is the RFC number, for example {\tt http://www.ietf.org/rfc/rfc2460.txt}
\bibitem{wdayperf} Plonka D, Barford P, Assessing performance of Internet services on IPv6, 2013 IEEE Symposium on Computers and Communications (ISCC), {\tt doi:10.1109/ISCC.2013.6755050}
%\bibitem{FTS3}
%    Salichos M, Keeble O, Alvarez Ayllon A, Kamil Simon M 2013 FTS3 - Robust, simplified and high-performance data movement service for WLCG {\it also presented at CHEP 2013}
\bibitem{Ayllon2014} {A A Ayllon and M Salichos and M K Simon and O Keeble} {\it {FTS}3: New Data Movement Service For {WLCG}}, {J. Phys.: Conf. Ser.} 2014, {\bf 513} 3 032081,  doi:{10.1088/1742-6596/513/3/032081}, {\tt{http://dx.doi.org/10.1088/1742-6596/513/3/032081}},
\bibitem{GFTP1.0} {\tt https://www.ogf.org/documents/GFD.20.pdf} 
\bibitem{GFTP2.0} {\tt https://www.ogf.org/documents/GFD.21.pdf} 
\bibitem{SRM2.2} {\tt http://sdm.lbl.gov/srm-wg/doc/SRM.v2.2.html}
\bibitem{perfsonar} B Tierney, J Metzger, J Boote, A Brown, M Zekauskas
J Zurawski, M Swany, M Grigoriev, perfSONAR: Instantiating a
Global Network Measurement Framework, 4th Workshop on Real Overlays and
Distributed Systems (ROADS’09) Co-located with the 22nd ACM Symposium
on Operating Systems Principles (SOSP), January 1, 2009.
\bibitem{wlcg-NTMG} S McKee, M Babik et al. Integrating network and
transfer metrics to optimize transfer efficiency and experiment workflows,
CHEP2015, Journal of Physics: Conference Series.



\end{thebibliography}
