\section*{References}

\begin{thebibliography}{1}
\bibitem{ipv6wg} {\tt http://hepix-ipv6.web.cern.ch}
\bibitem{rfc} All Internet Engineering Task Force Requests For Comments (RFC) documents are available
from URLs such as http://www.ietf.org/rfc/rfcNNNN.txt where NNNN is the RFC number, for example {\tt http://www.ietf.org/rfc/rfc2460.txt}
\bibitem{ipv6stat} See for instance {\tt http://www.google.com/ipv6/statistics.html}. The 2\% global connectivity threshold was crossed in September 2013.
\bibitem{rhel} {\tt http://www.redhat.com/products/enterprise-linux/}
\bibitem{cream}
C. Aiftimiei, P. Andreetto, S. Bertocco, S. Dalla Fina, A. Dorigo, E.
Frizziero, A. Gianelle, M. Marzolla, M. Mazzucato, M. Sgaravatto, S.
Traldi, L. Zangrando, Design and Implementation of the gLite CREAM Job
Management Service, Future Generation Computer Systems, Volume 26, Issue
4, April 2010, pp. 654-667, doi: 10.1016/j.future.2009.12.006.
\bibitem{wms}
M. Cecchi, F. Capannini, A. Dorigo, A. Ghiselli, F. Giacomini, A. Maraschini, M. Marzolla, S. Monforte, F. Pacini, L. Petronzio, F. Prelz, "The gLite Workload Management System, in proceeding of GPC 2009 conference
\bibitem{panda}
T Maeno 2008 "PanDA: distributed production and distributed analysis
system for ATLAS" J. Phys. Conf. Ser. 119 062036
\bibitem{fts}
The gLite File Transfer Service
P. Kunszt, P. Badino, R. Rocha, J. Casey, A. Frohner, G. McCance
In Workshop on Next Generation Distributed Data Management at HPDC06, Paris, France
\bibitem{phedgen}
Egeland R, Metson S and  Wildish T 2008 Data transfer infrastructure for
CMS data taking,  {\it XII Advanced Computing and Analysis Techniques in
Physics Research (Erice, Italy: Proceedings of Science)}
\bibitem{cvmfs}
Status and future perspectives of CernVM-FS
J Blomer et al 2012 J. Phys.: Conf. Ser. 396 052013
\bibitem{bdii}
Field, Laurence, and Markus W. Schulz. "Grid Deployment Experiences: The path to a production quality LDAP based grid information system." Proceedings of the International Conference on Computing in High Energy and Nuclear Physics (CHEP 2004). 2004.
\bibitem{monalisa}
Legrand I, Newman H, Voicu R, Cirstoiu C, Grigoras C, Dobre C, Muraru A,
Costan A, Dediu M and Stratan C 2009 MonALISA: An agent based, dynamic
service system to monitor, control and optimize distributed systems {\it
Computer Physics Communications, Volume 180, Issue 12, December 2009,
Pages 2472–2498}
\bibitem{LifeCycle}
    T. Wildish, {\it ``Integration and validation testing for PhEDEx, DBS and DAS with the PhEDEx LifeCycle agent''}, also presented at CHEP 2013
\bibitem{cms}
The CMS Collaboration 2008 The CMS experiment at the CERN LHC {\it JINST
{\bf 3} S08004}
\bibitem{PhEDEx}
    R. Egeland, T. Wildish, S. Metson, {\it ``2008 Data transfer infrastructure for CMS data taking''},  XII Advanced Computing and Analysis Techniques in Physics Research (Erice, Italy: Proceedings of Science)
\bibitem{FTS3}
    M. Salichos, O. Keeble, A. Alvarez Ayllon, M. Kamil Simon, {\it ``FTS3 - Robust, simplified and high-performance data movement service for WLCG"}, also presented at CHEP 2013.
\end{thebibliography}
